
```{r readingIn,cache=T}
datadir <- "./exampleFlowDataset2/"
souqce("./src/coulterZ2reader.R")
lrgdf <- coulterZ2reader(datadir)
```

This next part must be customized for your application! 
Look at the comments!

```{r formattingData,cache=T}
# here we put into the next column (ncol+1) through to 
#   enough columns (ncol+4), the colsplit of
lrgdf[,(ncol(lrgdf)+1):(ncol(lrgdf)+4)] <- colsplit(
# splitting the filename, sans extension, on underscores...
  string=sub(".=#Z2","",lrgdf$fz),pattern="_",
# and give them names for each field.
  names=c("date","time","media","blankOrNot"))
# for this to work, you have to have the same number of underscore
#   delimited fields in each filename. You can use something other
#   than underscore too, just change it in colsplit argument pattern
head(lrgdf)
```

```{r dataTypes,cache=T}
lrgdf$fz <- as.character(lrgdf$fz)
lrgdf$date <- as.Date(x=as.character(lrgdf$date),format="%y%m%d")
lrgdf$time <- 
  as.numeric(sub("(\\d{1,2})\\d{2}","\\1",lrgdf$time))*60+
  as.numeric(sub("\\d{1,2}(\\d{2})","\\1",lrgdf$time))
lrgdf$blankOrNot <- grepl("blank",lrgdf$blankOrNot)
lrgdf$media<-factor(lrgdf$media)
head(lrgdf)
```

For coulter, blanks are important to see how big the background
bubbles and crud are.

```{r gate,cache=T}
ggplot(lrgdf)+aes(x=bins,y=height,col=factor(time))+
	geom_point()+facet_wrap(~blankOrNot)+scale_y_log10()

ggplot(subset(lrgdf,bins>2.0))+aes(x=bins,y=height,col=factor(time))+
	geom_point()+facet_wrap(~blankOrNot)+scale_y_log10()

ggplot(subset(lrgdf,bins>2.5))+aes(x=bins,y=height,col=factor(time))+
	geom_point()+facet_wrap(~blankOrNot)+scale_y_log10()

ggplot(subset(lrgdf,bins>3.0))+aes(x=bins,y=height,col=factor(time))+
	geom_point()+facet_wrap(~blankOrNot)+scale_y_log10()

subdf <- subset(lrgdf,bins>2.5&bins<7.0&blankOrNot==F)
```

Below we use `aggregate` to just wrap up all events detected per
sample. Then we adjust by a scaling factor to adjust for the 
ammount counted, and the dilution factor. You will need to change
this!

```{r aggCounts,cache=T}
counts <- aggregate(height~fz+date+time+media,data=subdf,FUN=sum)
counts$e6cellsml <- counts$height/2000
# that adjustment must be adjusted!

g<-ggplot(counts)+
	aes(x=time/60,y=e6cellsml)+
	geom_point()+
	scale_y_log10(limits=c(1,7),breaks=seq(1,7,1))+
	scale_x_continuous(breaks=seq(09,21,1),labels=(09:21))+
	xlab("Hours")+
	ylab("million cells per ml")
g
#ggsave("151206exp152counts.pdf",g,width=8,height=6)
```

How about going back to distributions for alternative 
stats and representations?

```{r}
distributions <- list()
for (fz in unique(subdf$fz)) {
  distributions[[fz]] <- df2distribution(subset(subdf,fz==fz))
}
hist(distributions[[1]])
```


